The Rockerverse: Packages and Applications for Containerization with R

### 2020-01-28 manuscript.Rmd
ignore preprint file
document steps for submission to arXiv

rmarkdown::render("manuscript.Rmd", output_format = rjournal_style_preprint())
```

>>>>

rmarkdown::render("manuscript.Rmd", output_format = rjournal_style_preprint())
file.rename("RJwrapper.pdf", "rockerverse-preprint.pdf") # file for own archival

# for submission to arXiv, copy the following files into a new folder and run pdfLaTeX directly on RJwrapper.text (works with RStudio): figures/*, manuscript.tex, RJournal.sty, RJreferences.bib, RJwrapper.tex
# then tip the following files and submit to arXiv:
# - /figures
# - manuscript.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```
